\documentclass[11pt, oneside]{article}
\usepackage{kotex}
\title{Super Abstracted Programming Language}
\author{Dongjae Lee}
\date{2025.05.31}
\begin{document}
\maketitle

\begin{abstract}
	Programming languages have become increasingly abstracted over time. This is because advances in hardware and compilers have reduced the need to consider low-level elements when programming. As a result, productivity and efficiency have dramatically increased. Language models will push programming languages to an even higher level of abstraction, making programming tasks easier and more efficient.
\end{abstract}

In the past, due to limited hardware performance and compiler capabilities,
programmers had to develop software with hardware limitations in mind. As
hardware has advanced and compilers have added numerous functionalities, most
programmers no longer need to consider hardware. Thanks to this, software
development productivity has increased dramatically.

Abstraction, in other words, means not needing to specify the concrete
implementation details. Now, programmers are often not required to explicitly
define what sorting algorithm to use, how memory should be managed, or how
network communication should be handled, among other details.

Language models will enable programmers to program declaratively at a very high
level of abstraction. Compilers of existing programming languages translated
declarative elements into procedural machine code according to predetermined
rules. However, language models can understand user intent and convert it into
procedural algorithms even in situations where there are no predetermined
rules.

However, to ensure correctness, the accuracy of the converted algorithm must be
guaranteed. In the case of existing compilers, this is guaranteed through
numerous tests or verification techniques. However, since static inspection is
impossible for language models, it is necessary to dynamically check whether
the converted algorithm aligns with the user's intent. I would like to
guarantee correctness through \textsc{Expecto} and create a new programming
language and compiler based on \textsc{Expecto}.
\end{document}